\documentclass{beamer}
\usepackage[UTF8]{ctex}
\usetheme{default}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{listings}

\title{Security Matching System Present}
\author{Shen Guanzhi}
\begin{document}
\begin{frame}[plain]
    \maketitle
\end{frame}
\begin{frame}{Terms}
	\begin{itemize}
		\item Buy 买（动词）
		\item Sell 卖（动词）
		\item \textbf{Bid} Order 买单
		\item \textbf{Offer} Order 卖单
		\item Cancel Order 撤单
		\item Quantity 数量
		\item Call Auction 集合竞价
		\item Continuous Trade 连续竞价
		\item Quotations 行情
	\end{itemize}
\end{frame}
\begin{frame}{Question Analysis}
	Market Period
	\scalebox{0.6}{\input{market}}
\end{frame}
\begin{frame}{Question Analysis}
	Once Matching
	\scalebox{0.45}{\input{matches}}
\end{frame}
\begin{frame}{Question Analysis}
	\begin{table}[]
		\caption[]{Call Auction vs Continues Trade}
		\begin{tabular}{@{}|c|cc|@{}}
			\toprule
			Similarity                                                                                       & \multicolumn{2}{c|}{Differences}                                       \\ \midrule
			\multirow{4}{*}{\begin{tabular}[c]{@{}c@{}}Repetition of\\ Once Matching\\ Process\end{tabular}} & \multicolumn{1}{c|}{\multirow{2}{*}{Call Auction}}    & CPU-Intensive  \\ \cmidrule(l){3-3} 
			& \multicolumn{1}{c|}{}                                 & Non-Preemptive \\ \cmidrule(l){2-3} 
			& \multicolumn{1}{c|}{\multirow{2}{*}{Continues Trade}} & I/O-Intensive  \\ \cmidrule(l){3-3} 
			& \multicolumn{1}{c|}{}                                 & Preemptive     \\ \bottomrule
		\end{tabular}
	\end{table}
\end{frame}
\begin{frame}{Program Design: Book}
	The book of a security consist of a bid queue and a offer queue.
	\begin{table}[]
		\begin{tabular}{@{}lllll@{}}
			\toprule
			& Get Peak & Pop Peak & Insert   & Delete   \\ \midrule
			Binary Heap   & $O(1)$     & $O(\log n)$ & $O(\log n)$ & $O(n)$     \\
			Balanced Tree & $O(\log n)$ & $O(\log n)$ & $O(\log n)$ & $O(\log n)$ \\ \bottomrule
		\end{tabular}
	\end{table}
	It is not frequent to only get the peak value but not pop it. And delete value is also important.
	By use a balanced tree, quotations gotten by user are ordered.
\end{frame}
\begin{frame}{Program Design: Deal Maker}
	Each security has its own deal maker.
	\begin{itemize}
		\item Book
		\item Waiting Queue: Bids and offers which has been recorded to database but has not join the book.
		\item Watcher
		\item Auction Task: A coroutine trying to pop orders from the Waiting Queue and trade them or push them into the book.
	\end{itemize}
\end{frame}
\begin{frame}{Program Design: Deal Maker}
	There are some different coroutines wanting to read and write a deal maker, which is the main challenge of the whole system.
	\begin{itemize}
		\item Accept Task: Push an order into the waiting queue, and then suspense the calculate task and wake up the auction task.
		\item Auction Task: Pop orders from the waiting queue. While no waiting order, it should wake up the calculate task and suspend.
		\item Cancel Task: Try to remove order from the waiting queue. (Binary search. $O(\log n)$) If failing, then remove order from the book.
		\item Task which calculate opening or closing price: should wait for the waiting queue empty.
		\item View Task: Get the quotations at the present time.
	\end{itemize}
\end{frame}
\begin{frame}{Program Design: Deal Maker}
	The synchronizing algorithm should be both correct and fair.
	\begin{itemize}
		\item Both the book and the waiting queue are protected with R/W lock.
		\item The watcher is a special channel provided by the coroutine runtime.
	\end{itemize}
\end{frame}
\begin{frame}{Program Design: Deal Maker}
	\scalebox{0.4}{\input{auction}}
\end{frame}
\begin{frame}{Database Design}
	\scalebox{0.35}{\input{security_matching}}
	\begin{itemize}
		\item While \lstinline|order| and \lstinline|msg| tables are used to backup data in memory, \lstinline|req| and \lstinline|res| tables are used to save user order requirement and trade record.
		\item Transaction is utilized.
	\end{itemize}
\end{frame}
\end{document}
